An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2019-07-08 jmiv.tex
fatigue

We present an application of our digital curve evolution algorithm to supervised image segmentation. The DCE will act as a contour correction method. Here we are going to use a data fidelity term in order to characterize the object of interest. Given foreground and background seeds selected by the user, we derive mixed gaussian distributions  of color intensities $G_f$ and $G_b$, and we define the data fidelity term as

>>>>

We present an application of our digital curve evolution algorithm to supervised image segmentation. The DCE acts as a
contour correction method. Here we are going to use a data fidelity term in order to characterize the object of
interest. Given foreground and background seeds selected by the user, we derive mixed gaussian distributions  of color
intensities $G_f$ and $G_b$, and we define the data fidelity term as the cross-entropy, i.e.
